dendro

### 2017-05-31 analysis/analysis_chronologies.Rmd
update
update messages
update boot CI

@@

```{r}
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/chrono_bai.R'))
source(paste0(di, 'script/R/suaviza_cronos.R'))
```

@@

## Compute similarity between chronos 
Use @Dorado2017 approach.

@@

```{r}
# centred moved average smooth
suaviza_caH <- suaviza_cronos(cro_caH, win_vector=seq(1,40, by=1), crononame = 'cro_caH')
suaviza_caL <- suaviza_cronos(cro_caL, win_vector=seq(1,40, by=1), crononame = 'cro_caL')
suaviza_sjH <- suaviza_cronos(cro_sjH, win_vector=seq(1,40, by=1), crononame = 'cro_sjH')
suaviza_sjL <- suaviza_cronos(cro_sjL, win_vector=seq(1,40, by=1), crononame = 'cro_sjL')

@@

### Bootstrap IC

```{r}
# Metodo correlation
tipos_correla <- c('spearman', 'pearson')

for (m in tipos_correla){

  metodo_correla <- m

suaviza_sj <- rbind(suaviza_sjH, suaviza_sjL)

out_final <- c()

for (j in 1:40){

  aux <- suaviza_sj  %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    na.omit() %>% # to compare the series in the years they are overlapping 
    as.data.frame()

  # Put years as rownames and delete yearss variable
  rownames(aux) <- aux$yearss 
  aux1 <- aux[,-1]

  # Names the series 
  names(aux1) <- c('H', 'L')

  # Get real value of correlation between smoothed series 
  pearson <- cor.test(aux1$H, aux1$L, method = metodo_correla)$estimate

  ## Bootstratp to ger CI 
  correlationTest <- function(x,index){
    ct <- cor.test(x$H[index], x$L[index], method = metodo_correla)
    return(ct$estimate)
    }

  ### boostrap   
  boot_cor <- boot(aux1, correlationTest, R=1000)
  ### CI
  bci <- boot.ci(boot_cor, conf = 0.95, type = 'bca')

  # Output results 
  estimate <- bci$t0 # Pearson coefficient
  ci_lower <- bci$bca[4] # Lower CI
  ci_upper <- bci$bca[5] # Upper CI

  out <- as.data.frame(cbind(estimate, 
                             ci_lower, 
                             ci_upper))
  # Smoothing year (window size)
  out$size <- j

  out_final <- rbind(out_final, out)

}

out_final$site <- 'SJ'
correla_sj <- out_final

# CA
suaviza_ca <- rbind(suaviza_caH, suaviza_caL) 
out_final <- c()

for (j in 1:40){

  aux <- suaviza_ca  %>% 
    filter(size_wind == j) %>%
    select(-size_wind) %>% 
    spread(crononame, bai_smooth) %>% 
    na.omit() %>% # to compare the series in the years they are overlapping 
    as.data.frame()

  # Put years as rownames and delete yearss variable
  rownames(aux) <- aux$yearss 
  aux1 <- aux[,-1]

  # Names the series 
  names(aux1) <- c('H', 'L')

  # Get real value of correlation between smoothed series 
  pearson <- cor.test(aux1$H, aux1$L, method = metodo_correla)$estimate

  ## Bootstratp to ger CI 
  correlationTest <- function(x,index){
    ct <- cor.test(x$H[index], x$L[index], method = metodo_correla)
    return(ct$estimate)
    }

  ### boostrap   
  boot_cor <- boot(aux1, correlationTest, R=1000)
  ### CI
  bci <- boot.ci(boot_cor, conf = 0.95, type = 'bca')

  # Output results 
  estimate <- bci$t0 # Pearson coefficient
  ci_lower <- bci$bca[4] # Lower CI
  ci_upper <- bci$bca[5] # Upper CI

  out <- as.data.frame(cbind(estimate, 
                             ci_lower, 
                             ci_upper))
  # Smoothing year (window size)
  out$size <- j

  out_final <- rbind(out_final, out)

}

out_final$site <- 'CA'
correla_ca <- out_final

# Combine datasets and plot coefficient correlation 
correla <- rbind(correla_ca, correla_sj) 
correla$metodo_correla <- metodo_correla
assign(paste0('correla_', metodo_correla), correla)
}

### Plot similarity among chronologies

```{r, fig.width=12, fig.height=8}
correla <- rbind(correla_pearson, correla_spearman)
correla$series <- ifelse(correla$site == 'CA', 
                         'CAHigh-CALow',
                         'SJHigh-SJLow')

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=series)) + geom_line()+
  theme_bw() + 
  ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=series), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=series), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,warning=FALSE, message=FALSE)
```

@@

```{r}
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/chrono_bai.R'))
source(paste0(di, 'script/R/suaviza_cronos.R'))
source(paste0(di, 'script/R/correlaBootIC.R'))
```

@@

# Correlation between chronos

To compute similarity between chronos we use @Dorado2017 approach.

@@

```{r}
# centred moved average smooth
suaviza_caH <- suaviza_cronos(cro_caH, win_vector=seq(1,40, by=1), crononame = 'cro_caH')
suaviza_caL <- suaviza_cronos(cro_caL, win_vector=seq(1,40, by=1), crononame = 'cro_caL')
suaviza_sjH <- suaviza_cronos(cro_sjH, win_vector=seq(1,40, by=1), crononame = 'cro_sjH')
suaviza_sjL <- suaviza_cronos(cro_sjL, win_vector=seq(1,40, by=1), crononame = 'cro_sjL')
```

## between sites similarity (sjH *vs* sjL; caH *vs* caL)

This note is for the plot:

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
# Metodo correlation
tc <- c('spearman', 'pearson')

# SJ 
suaviza_sj <- rbind(suaviza_sjH, suaviza_sjL)
correla_sj <- correlaBootIC(suaviza_sj, tc, years_suavizado = 40, 
                            name_comparison = 'sjH-sjL')

# CA 
suaviza_ca <- rbind(suaviza_caH, suaviza_caL)
correla_ca <- correlaBootIC(suaviza_ca, tc, years_suavizado = 40, 
                            name_comparison = 'caH-caL')

correla <- rbind(correla_ca, correla_sj)

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())

@@

## between final sites similarity (sj *vs* caH; sj *vs* caL; caH *vs* caL)

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
# Metodo correlation
tc <- c('spearman', 'pearson')

# Compute the suaviza_sj desde el principio, sin diferenciar h and l. Para ello la crono la computo de nuevo 
cro_sjloc <- chrono_bai(bai_sj)
cro_sjloc$site <- 'SJ'
suaviza_sjloc <- suaviza_cronos(cro_sjloc, win_vector=seq(1,40, by=1), crononame = 'cro_sj')

# sjcaH 
suaviza_sjcaH <- rbind(suaviza_sjloc, suaviza_caH)
correla_sjcaH <- correlaBootIC(suaviza_sjcaH, tc, years_suavizado = 40, 
                            name_comparison = 'sj-caH')

# sjcaL 
suaviza_sjcaL <- rbind(suaviza_sjloc, suaviza_caL)
correla_sjcaL <- correlaBootIC(suaviza_sjcaL, tc, years_suavizado = 40, 
                            name_comparison = 'sj-caL')

# Join all correlations 
correla <- rbind(correla_ca, correla_sjcaL, correla_sjcaH)

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())
```

---> here
